### 2013-06-19 Tex/chapters/model.tex
Bessere Formulierungen und Korrekturen.

%~ \subsubsection{Graphs}
    %~ A graph is a set of nodes \(V\) and edges \(E\).
\subsection{Gabriel- and Relative Neighborhood Graph}
\label{ssec:graphtypes}
    All here mentioned graph types are \emph{proximity graphs}. They are
    connecting nodes which are by some metric near to each other.
    Hence they are suited to generalize problems defined on regular
    lattices with nearest neighbor relationships, like the Ising model
    which will be described in more detail in section
    \ref{ssec:isingmodel}.\\
    The Gabriel Graph \cite{Gabriel1969} is a subgraph of the
    Delaunay Triangulation. Two nodes \(i\) and \(j\) with distance
    \(d_{ij}\) are connected with an edge if a circle with it's
    center on the middlepoint between \(i\) and \(j\) and radius
    \(r = \frac d 2\) contains no other nodes. This area will be
    called \emph{lune} in the following. See also Figure
    \ref{fig:lunes}\subref{sfig:lunes:def}.\\
    The Relative Neighborhood Graph \cite{Toussaint1980} is a
    subgraph of the Gabriel Graph. Two nodes \(i\) and \(j\) with
    distance \(d_{ij}\) are connected if no other node is in the
    \emph{lune}. The lune is defined as the intersection of two
    circles with radius \(r = d\) and centers on \(i\) and \(j\).
    See also Figure \ref{fig:lunes}\subref{sfig:lunes:def}.
    \begin{figure}[htbp]
        \centering
        \subfigure[Definition of the lunes][]{
                \label{sfig:lunes:def}
                \input{images/GG_RNG_def}
        }
        \subfigure[Relative Neighborhood graph example][]{
                \label{sfig:lunes:rng}
                \includegraphics[width=0.3\textwidth]{images/RNG/L12S03.pdf}
        }
        \subfigure[Gabriel graph example][]{
                \label{sfig:lunes:gg}
                \includegraphics[width=0.3\textwidth]{images/GG/L12S03.pdf}
        }
        \caption[Gabriel - and Relative Neighborhood Graph]
                {\subref{sfig:lunes:def} Lunes of Relative Neighborhood
                    Graph (hatched region) and
                    Gabriel Graph (cross hatched region)
                 \subref{sfig:lunes:def} Example of a Relative
                    Neighborhood Graph on periodic boundary conditions.
                    Periodic nodes are dashed.
                 \subref{sfig:lunes:gg} Example of a Gabriel Graph on
                    periodic boundary conditions. Periodic nodes are
                    dashed.
                }
        \label{fig:lunes}

@@

\subsection{Model}
\label{ssec:isingmodel}
    The used model is a modified 2D Ising model where the \(N\) sites
    are displaced nodes of a square lattice of edge length \(L\) with
    periodic boundary conditions. The displacement is randomly gauss
    distributed with the standard deviation \(\sigma\). This \(\sigma\)
    is also called \emph{disturbance paramter} in the following.
    The hamiltonian of the Ising model is
    \(\hat{H} = \sum_{\avg{i,j}}J_{ij}s_{i}s_{j}\)
    where \(\avg{i,j}\) refers to nodes connected  by edges.
    The edges are constructed according to the in section
    \ref{ssec:graphtypes} defined rules. So that the lattice resembles a
    proximity graph. Each node \(i\) has a spin \(s_i = \pm 1\). Each
    edge has a weight \(J_{ij} = \exp (\alpha (1-d_{ij}))\) with the
    distance \(d_{ij}\) between the nodes \(i\) and \(j\) and
    \(\alpha = 0.5\). \(J\) is called \emph{coupling constant}.\\
    For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),
    for which exists an analytical solution \cite{Onsager1944}.\\

@@

\subsection{Critical Temperature $T_c$ and Critical Exponents}
\label{ssec:finitesize}
    The searched for property -- the critical temperature \(T_c\)
    -- is only defined for infinite systems, hence every computer
    simulation will show some \emph{finte size effects}.
    %[vielleicht Bild von intensiver Größe?]
    Despite of this one can obtain \(T_c\) by finite size scaling
    methods \cite[S. ??]{NewmanBarkema1999} which also yield the critical
    exponents. The critical exponents should not be influenced by the
    disturbance paramter \(\sigma\) [citation needed]. So they will be
    used for consistency cross checking and comparision with the known
    exact values \cite[S. 59]{Pelissetto2002}.\\
    %~ [theorie mit dem Collaps]
    %~ [Erklaerung: was sind beta, gamma, nu]
    To accomplish the collapse in an semi-automatic and reproduceable
    way with an error estimate, the programm
    \texttt{autoscale.py} \cite{autoscale2009} is used.
    %~ [Erklärung autoscale]
    %~ [Am besten hier direkt die ganze Auswertung rein]
    %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma die exponenten reproduziert hat].\\
    \begin{figure}[htbp]
        \centering
        \subfigure[Example of a Binder cumulant to determine the critical temperature][]{
                \label{sfig:binder_fit_s_0}
                \includegraphics[width=0.47\textwidth]{plots/binder_fit_s_0}
        }
        \subfigure[Example of a datacollapse to determine critical exponents][]{
                \label{sfig:collapse_s_0}
                \includegraphics[width=0.47\textwidth]{plots/collapse_s_0}
        }
        \caption[Examples of determining critical temperature and exponents]
                {\subref{sfig:binder_fit_s_0} Binder cumulant interpolated
                    with cubic splines (the errorbars are too small to see)
                 \subref{sfig:collapse_s_0} Collapse of the Binder cumulant
                }
        \label{fig:binder_fit_s_0}
    \end{figure}\\
    Though if one is just interested in the critical Temperature, an
    easier approach is to find the intersections of the Binder cumulants
    \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} of different
    system sizes \(L=\sqrt N\).
    Therefore a cubic spline interpolation is calculated\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
    for the measured points.
    In fig. \ref{fig:binder_fit_s_0} such an interpolation is plotted for
    \(\sigma=0\). The cumulants intersect at \(\approx 2.27 k_{B}\). For
    the sake of simplicity let the Boltzmann constant \(k_{B}=1\) in the
    following.
    To determine \(T_c\) the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}
    are averaged and the standard
    error is calculated. In this case one gets \(T_c = 2.2689\pm0.0002\),
    which is in good agreement with the exact solution
    \(T_c = 2.2691...\) \cite{Onsager1944}.\\
    Because \(T_{c}\) is dependend on \(J\) and hence also on the count
    of bounds, the values of \(T_{c}\) will be normalized by the mean
    sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\).

>>>>

%~ \subsubsection{Graphs}
    %~ A graph is a set of nodes \(V\) and edges \(E\).
\subsection{Gabriel- and Relative Neighborhood Graph}
\label{ssec:graphtypes}
    All here mentioned graph types are \emph{proximity graphs}. They are
    connecting nodes which are by some metric near to each other.
    Hence they are suited to generalize problems defined on regular
    lattices with nearest neighbor relationships, like the Ising model
    which will be described in more detail in section
    \ref{ssec:isingmodel}.\\
    The Gabriel Graph \cite{Gabriel1969} is a subgraph of the
    Delaunay Triangulation. Two nodes \(i\) and \(j\) with distance
    \(d_{ij}\) are connected with an edge if a circle with it's
    center on the middlepoint between \(i\) and \(j\) and radius
    \(r = \frac d 2\) contains no other nodes. This area will be
    called \emph{lune} in the following. See also Figure
    \ref{fig:lunes}\subref{sfig:lunes:def}.\\
    The Relative Neighborhood Graph \cite{Toussaint1980} is a
    subgraph of the Gabriel Graph. Two nodes \(i\) and \(j\) with
    distance \(d_{ij}\) are connected if no other node is in the
    \emph{lune}. The lune is defined as the intersection of two
    circles with radius \(r = d\) and centers on \(i\) and \(j\).
    See also Figure \ref{fig:lunes}\subref{sfig:lunes:def}.
    \begin{figure}[htbp]
        \centering
        \subfigure[Definition of the lunes][]{
                \label{sfig:lunes:def}
                \input{images/GG_RNG_def}
        }
        \subfigure[Relative Neighborhood graph example][]{
                \label{sfig:lunes:rng}
                \includegraphics[width=0.3\textwidth]{images/RNG/L12S03.pdf}
        }
        \subfigure[Gabriel graph example][]{
                \label{sfig:lunes:gg}
                \includegraphics[width=0.3\textwidth]{images/GG/L12S03.pdf}
        }
        \caption[Gabriel - and Relative Neighborhood Graph]
                {\subref{sfig:lunes:def} Lunes of Relative Neighborhood
                    Graph (hatched region) and
                    Gabriel Graph (cross hatched region)
                 \subref{sfig:lunes:rng} Example of a Relative
                    Neighborhood Graph on periodic boundary conditions.
                    Periodic nodes are dashed.
                 \subref{sfig:lunes:gg} Example of a Gabriel Graph on
                    periodic boundary conditions. Periodic nodes are
                    dashed.
                }
        \label{fig:lunes}

@@

\subsection{The Disturbed Ising Model}
\label{ssec:isingmodel}
    The used model is a modified 2D Ising model where the \(N=L^2\) sites
    are displaced nodes of a square lattice of edge length \(L\) with
    periodic boundary conditions. The displacement is randomly gauss
    distributed with the standard deviation \(\sigma\). This \(\sigma\)
    is also called \emph{disturbance paramter} in the following.
    The hamiltonian of the Ising model is
    \(\hat{H} = \sum_{\avg{i,j}}J_{ij}s_{i}s_{j}\)
    where \(\avg{i,j}\) refers to nodes connected  by edges.
    The edges are constructed according to the in section
    \ref{ssec:graphtypes} defined rules. So that the lattice resembles a
    proximity graph. Each node \(i\) has a spin \(s_i = \pm 1\). Each
    edge has a weight \(J_{ij} = \exp (\alpha (1-d_{ij}))\) with the
    distance \(d_{ij}\) between the nodes \(i\) and \(j\) and
    \(\alpha = 0.5\). \(J\) is called \emph{coupling constant}.\\
    For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),
    for which exists an analytical solution \cite{Onsager1944}.\\

@@

\subsection{Critical Temperature $T_c$ and Critical Exponents}
\label{ssec:finitesize}
    The searched for property -- the critical temperature \(T_c\)
    -- is only defined for infinite systems, hence every computer
    simulation will show some \emph{finte size effects}.
    %[vielleicht Bild von intensiver Größe?]
    Despite of this one can obtain \(T_c\) by finite size scaling
    methods \cite[S. ??]{NewmanBarkema1999} which also yield the critical
    exponents. The critical exponents should not be influenced by the
    disturbance paramter \(\sigma\) [citation needed]. So they will be
    used for consistency cross checking and comparision with the known
    exact values \cite[S. 59]{Pelissetto2002}.\\
    %~ [theorie mit dem Collaps]
    %~ [Erklaerung: was sind beta, gamma, nu]
    To accomplish the collapse in an semi-automatic and reproduceable
    way with an error estimate, the programm
    \texttt{autoscale.py} \cite{autoscale2009} is used.
    %~ [Erklärung autoscale]
    %~ [Am besten hier direkt die ganze Auswertung rein]
    %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma die exponenten reproduziert hat].\\
    \begin{figure}[htbp]
        \centering
        \subfigure[Example of a Binder cumulant to determine the critical temperature][]{
                \label{sfig:gettingCrit:binder_fit_s_0}
                \includegraphics[width=0.47\textwidth]{plots/binder_fit_s_0}
        }
        \subfigure[Example of a datacollapse to determine critical exponents][]{
                \label{sfig:gettingCrit:collapse_s_0}
                \includegraphics[width=0.47\textwidth]{plots/collapse_s_0}
        }
        \caption[Examples of determining critical temperature and exponents]
                {The Binder cumulant \(g\) of an square lattice Ising model
                 (\(\sigma=0\))\\
                 \subref{sfig:gettingCrit:binder_fit_s_0} interpolated
                    with cubic splines (the errorbars are too small to see)\\
                 \subref{sfig:gettingCrit:collapse_s_0} collapsed by finite
                    size scaling
                }
        \label{fig:gettingCrit}
    \end{figure}\\
    Though if one is just interested in the critical Temperature, an
    easier approach is to find the intersections of the Binder cumulants
    \(g\) of different system sizes \(L\).
    Therefore a cubic spline interpolation is calculated\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
    for the measured points.
    In fig. \ref{fig:gettingCrit}\subref{fig:gettingCrit:binder_fit_s_0}
    such an interpolation is plotted for \(\sigma=0\). The cumulants
    intersect at \(\approx 2.27 k_{B}\). For the sake of simplicity let
    the Boltzmann constant \(k_{B}=1\) in the following.
    To determine \(T_c\) the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}
    are averaged and the standard error is calculated. In this case one
    gets \(T_c = 2.2689\pm0.0002\), which is in good agreement with the
    exact solution
    \begin{equation}
        T_c = 2J/\ln(1+\sqrt 2) = 2.2691... \cite{Onsager1944}
        \label{eq:exactTc}
    \end{equation}

### 2013-06-19 Tex/chapters/results.tex
Bessere Formulierungen und Korrekturen.

\subsection{Critical Temperature}
    The evaluation of the Binder cumulant's intersections, yields the
    critical temperatures \(T_c\), which are normalized and plotted in
    fig. \ref{fig:Tc}.
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:Tc:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm}
        }
        \subfigure[][]
        {
            \label{sfig:Tc:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm}
        }
        \caption[Critical Temperature over different disturbance parameters]
                {Normalized critical temperatures over different
                 disturbance parameters for
                 \subref{sfig:Tc:RNG} the Relative Neighborhood Graph and
                 \subref{sfig:Tc:GG} the Gabriel Graph.
                }
        \label{fig:Tc}
    \end{figure}
    % I don't know what all that means...

>>>>

\subsection{Critical Temperature}
    The evaluation of the Binder cumulant's intersections, yields the
    critical temperatures \(T_c\), which are plotted in
    fig. \ref{fig:Tc}\subref{sfig:Tc:RNG}\subref{sfig:Tc:GG}.
    Further in fig. \ref{fig:Tc}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
    the mean sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
    is plotted which is evidently correlated with \(T_c\).
    That is plausible, because \(T_c\) is dependend on the coupling
    constant \(J\) (compare \eqref{eq:exactTc}).\\
    It seems reasonable to normalize the values of \(T_{c}\) by
    \(\avg{\sum_{\avg{i,j}} J_{ij}}\) which yields the diagramms fig.
    \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}\subref{sfig:Tc_norm:GG}.

    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:Tc:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc}
        }
        \subfigure[][]
        {
            \label{sfig:Tc:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_Tc}
        }

        \subfigure[][]
        {
            \label{sfig:sumJ:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_sumJ}
        }
        \subfigure[][]
        {
            \label{sfig:sumJ:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_sumJ}
        }

        \subfigure[][]
        {
            \label{sfig:Tc_norm:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm}
        }
        \subfigure[][]
        {
            \label{sfig:Tc_norm:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm}
        }
        \caption[Critical Temperature over different disturbance parameters]
                {Top: Critical temperatures over different
                 disturbance parameters for
                 \subref{sfig:Tc:RNG} the Relative Neighborhood Graph and
                 \subref{sfig:Tc:GG} the Gabriel Graph.\\
                 Middle: Degree over different disturbance parameters for
                 \subref{sfig:deg:RNG} the Relative Neighborhood Graph and
                 \subref{sfig:deg:GG} the Gabriel Graph.\\
                 Bottom: Normalized critical temperatures over different
                 disturbance parameters for
                 \subref{sfig:Tc_norm:RNG} the Relative Neighborhood Graph and
                 \subref{sfig:Tc_norm:GG} the Gabriel Graph.
                }
        \label{fig:Tc}
    \end{figure}
    % I don't know what all that means...
